Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-22 outputs/paper/paper.Rmd
Data session writing (3)

# Appendix {-}

>>>>

# Appendix {-}
In this session, I am going to deal with remained data explanation. Since no dramatic changes were observed in remained variables, I combined them by patterns.

1) Decrease in "Too little" and increase in "About right" and "Too much"

- Big cities Problems (figure \@ref(fig:fig4))
- Education (figure \@ref(fig:fig7))

2) Decrease in "Too little" and "About right" and increase in "Too much"

- Childcare (figure \@ref(fig:fig3))
- Crime rates (figure \@ref(fig:fig5))
- New energy (figure \@ref(fig:fig8))
- Social security (figure \@ref(fig:fig17))

3) Decrease in "About right" and increase in "Too little" and "Too much"

- Environment (figure \@ref(fig:fig9))

4) Decrease in "Too much" and increase in "Too little and "About right"

- Road (figure \@ref(fig:fig15))

4) only subtle changes.

- Mass transportation (figure \@ref(fig:fig12))
- Park and Recreation (figure \@ref(fig:fig13))
- Scientific research (figure \@ref(fig:fig16))
